\documentclass[ignorenonframetext,]{beamer}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\newif\ifbibliography
\hypersetup{
            pdftitle={Peer Production Project: API Samples of Digital Public Library of America},
            pdfauthor={Yu Zhang},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

% Prevent slide breaks in the middle of a paragraph:
\widowpenalties 1 10000
\raggedbottom

\AtBeginPart{
  \let\insertpartnumber\relax
  \let\partname\relax
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \let\insertsectionnumber\relax
    \let\sectionname\relax
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \let\insertsubsectionnumber\relax
  \let\subsectionname\relax
  \frame{\subsectionpage}
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

\title{Peer Production Project: API Samples of Digital Public Library of
America}
\author{Yu Zhang}
\date{5/1/2018}

\begin{document}
\frame{\titlepage}

\begin{frame}{Introduction}

\begin{itemize}
\tightlist
\item
  DPLA
\end{itemize}

Digital Public Library of America is is public domain and openly
licensed content held by the United States' archives, libraries,
museums, and other cultural heritage institutions. It has a large and
complete Hub network to collect data.

\begin{itemize}
\tightlist
\item
  APIs
\end{itemize}

DPLA's API provides programmatic search and access to every item in the
DPLA catalog. Use the API to power an app, to wire DPLA into your
portal, or to retrieve data to build something entirely your own. DPLA
also providers complete API tutorial to get you started

\end{frame}

\begin{frame}{The Workflow of How DPLA Collects Items}

\end{frame}

\begin{frame}{What did I do}

The function I planed to implement is getting the list of provider and
dataProvider. I went through the API document and Metadata Application
Profile, and figure out what information each item contains as metadata.
And then I tried to find which interface I should use, and studied what
workflow and algorithm should be in my code, and how providers relate to
dataProviders. Finally when I implemented the function and debugged, I
put all the sample in one package and run them together, to see whether
there is a conflict or not.

\end{frame}

\begin{frame}{The result}

Here are the results:

\begin{itemize}
\tightlist
\item
  Provider list
\end{itemize}

\begin{itemize}
\tightlist
\item
  dataProvider list
\end{itemize}

\end{frame}

\begin{frame}{Thank you}

Thanks for Watching!

\end{frame}

\end{document}
